Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-02 sattose/paper.tex
Magiel paper

\section{Introduction}
Duplication in source code is often seen as one of the most harmful types of technical debt. In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
% In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

@@

Code clones can be found anywhere in a codebase. The location of a clone in the code has an impact on how it can be refactored. Therefore, we first look at where and how often clones are found, enabling the prioritization of refactoring opportunities.

@@

Our end goal is to improve upon the current state-of-the-art in clone research~\cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found. The design decisions for this tool are made on basis of data gathered from a large corpus of software systems together with our own experience and findings from literature.

@@

For \textbf{RQ1} we look into current clone definitions and clone detection methods. We then assess their suitability for refactoring purposes. For \textbf{RQ2} we look into what thresholds we should use to identify clones that, when refactored, improve the design of the system. \textbf{RQ3} is currently work in progress.

>>>>

\section{Introduction}
Duplication in source code is often seen as one of the most harmful types of technical debt. In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}. A paper by Bruntink et al.~\cite{bruntink2005use} shows that code clones can contribute up to 25\% of the code size, which has a negative impact on the maintainability.
% In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

@@

@@

Our end goal is to improve upon the current state-of-the-art in clone research~\cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that can analyze the context of code clones to get a profile of how a clone can be refactored. This tool then automatically applies refactorings to a large percentage of clones found. The design decisions for this tool are made on basis of data gathered from a large corpus of software systems together with our own experience and findings from literature.

@@

For \textbf{RQ1} we look into current clone definitions and clone detection methods and assess their suitability for refactoring purposes. For \textbf{RQ2} we look into what thresholds we should use to identify clones that, when refactored, improve the design of the system. \textbf{RQ3} is currently work in progress.
